%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {NEAR Digital Collective}{Aug 2023 -- Present}
    {Test Automation Engineer $|$ \emph{Cypress, Postman, Jest, Supertest, Node.js }}{Remote}
    \resumeItemListStart
        \resumeItem{Developed and maintained a regression test suite using Cypress. Ensured test coverage, and integrated them into a CICD pipeline, improving software release efficiency by 35\% within the first quarter.}
        \resumeItem{Wrote Postman scripts to validate rest APIs, ensuring endpoint authorization and functionality.}
        \resumeItem{Wrote API automation tests with Jest and Supertest.}
    \resumeItemListEnd

    \resumeSubheading
    {Lumeris}{Sept 2021 -- Feb 2023}
    {Software Engineer}{Morriseville, NC}
    \resumeItemListStart
        \resumeItem{Developed and maintained the internal Sysadmin platform, built with Django, Jquery, and Javascript.}
        \resumeItem{Wrote Vue JS components for the chat platform on the Lumeris Engage site allowing for secure patient-doctor communications. }
        \resumeItem{Managed and expanded unit tests, and designed components in a shared UI library.}
    \resumeItemListEnd

    \resumeSubheading
    {Mako Medical}{Sept 2019 -- Sept 2021}
    {Jr Software Engineer}{Raleigh, NC}
    \resumeItemListStart
        \resumeItem{Developed a scheduling platform to organize public testing locations and appointments during the COVID-19 pandemic. Built with Django, JQuery and Bootstrap.}
        \resumeItem{Developed the Mako Exchange platform enabling efficient testing and resulting of thousands of patients' samples.  Built with Django, JQuery  and Bootstrap.}
        \resumeItem{Implemented integration processes, streamlined interfaces with EMRs, and ensured adherence to healthcare data standards using Mirth and HL7.}
    \resumeItemListEnd

\resumeSubHeadingListEnd